\documentclass{llncs}
\usepackage{times,url,comment}
\usepackage{amsmath,amssymb,amsfonts,bbm}
\usepackage{graphicx,epsfig,epsf}
\usepackage{alltt}
\usepackage{url}
\usepackage{cite}
 
   
% mix and mac
\usepackage[latin1]{inputenc}
\usepackage{comment}
\usepackage{algorithm}
\usepackage[usenames]{color}

 

%%%
\newcommand{\ie}{i.e.}
\newcommand{\eg}{e.g.}
\newcommand{\vs}{vs.}

\newcommand{\verbi}[1]{{\small\texttt{#1}}}


%% Intra nos
\newcommand{\Ce} [1]{{[\color{cyan}{Cédric}}: {#1}]}
\newcommand{\Fr} [1]{{[\color{blue}{Francesco}}: {#1}]}
\newcommand{\Gi} [1]{{[\color{red}{Gigi}}: {#1}]}
\newcommand{\Bo} [1]{{[\color{green}{Bojan}}: {#1}]}
\newcommand{\La} [1]{{[\color{pink}{Laurent}}: {#1}]}
\newcommand{\Vi} [1]{{[\color{cyan}{Vincenzo}}: {#1}]}

\newcommand{\RESP} [1]{{[\color{red}{RESP: #1}]}}




%% High penalties for line and paragraph-breaking [Dan]
\pretolerance=2000 \binoppenalty=2000 \relpenalty=1500
%\interlinepenalty=150 \predisplaypenalty=10000 \postdisplaypenalty=400
\hbadness=5000 \hfuzz=2pt 



%%%% FORMATTING
\newcommand{\rew}[1]   {\hspace{-#1mm}}
\newcommand{\fwd}[1]   {\hspace{#1mm}}
\newcommand{\down}[1]  {\vspace{#1mm}}
\newcommand{\up}[1]    {\vspace{-#1mm}}

\include{algorithmic_header}
 
 \title{Synapse: A Scalable Protocol for Interconnecting Heterogeneous
   Overlay Networks\thanks{Supported by AEOLUS
     FP6-IST-15964-FET Proactive and DEUKS JEP-41099 TEMPUS.} \up{4}}
% %
 \author{Luigi Liquori \inst{1}\thanks{Corresponding author.  Thanks
     to Ernst Biersack for the precious discussions.} \and C\'edric Tedeschi \inst{2} \and
   Laurent Vanni \inst{1}
   \and \\
   Francesco Bongiovanni\inst{1} \and Vincenzo Ciancaglini\inst{1}
   \and Bojan Marinkovic \inst{3}}

\institute{Institut National de Recherche en Informatique et
  Automatique, France\\
  Email: {\tt firstName.lastName@sophia.inria.fr} \and
  Universit\'e de Rennes I/INRIA, France\\ 
  Email: {\tt Cedric.Tedeschi@inria.fr} \and
  Mathematical Institute of the Serbian Academy of Sciences and Arts, Serbia\\
  Email: {\tt bojanm@turing.mi.sanu.ac.rs}}

\pagestyle{plain}
\sloppy

\begin{document}


\maketitle
  
\begin{abstract}\up{4}
  This\,paper\,presents\,Synapse,\,a\,scalable\,protocol\,for\,information
  retrie\-val
  over\,the\,inter-connection\,of\,heterogeneous\,overlay\,networks. Applications\,on
  top of Synapse\,see\,those\,intra-overlay
  networks\,as\,a\,unique\,inter-overlay network.

  Scalability in Synapse is achieved via co-located nodes, \ie\ nodes
  that are part of multiple overlay networks at the same time.
  Co-located nodes, playing the role of \emph{neural synapses} and
  connected to several overlay networks, give a larger search area
  and provide alternative routing.  

  Synapse can either work with ``open'' overlays adapting their
  protocol to synapse interconnection requirements, or with ``closed''
  overlays that will not accept any change to their protocol.

  % Synapse\,can\,work\,either\,with\,``open''\,overlays\,that\,could\,adapt\,their\,protocol\,or\,with
  % ``closed''\,overlays\,that\,only\,route\,according\,to\,their\,protocol.
  % Built-in primitives to deal with social networking
  % give an incentive for nodes cooperation.% between nodes.
  %
  Results from simulation and experiments show that Synapse is
  scalable, with a communication and state overhead scaling similarly
  as the networks interconnected. thanks to alternate routing paths,
  Synapse also gives a practical solution to network partitions.

%  cost\,scaling\,with\,the\,same\,complexity\,of\,the\,connected\,networks. Because
%  of alternative routing, Synapse gives also a practical solution to
%  network partitions.

  We precisely capture the behavior of traditional metrics of overlay
  networks within Synapse and present results from simulations as well
  as some actual experiments of a client prototype on the Grid'5000
  platform. The prototype developed implements the Synapse protocol in
  the particular case of the inter-connection of many Chord overlay
  networks.

  \smallskip {\bf Keywords.} Peer to peer, overlay networks,
  information retrieval.  \up{2}
\end{abstract}

  
\up{4}
\section{Introduction}
\up{3}
\input{intro}
\up{3}
\section{The Synapse Protocol\label{sec:protocol}}
\up{3}
\input{protocol}
\up{3}
\section{The Simulations\label{sec:simulations}}
\up{3}
\input{simulation}
\section{The Experimentations\label{sec:deployement}}
\up{3}
\input{deployement}
\up{3}
\section{Related Work\label{sec:relatedwork}}
\up{3}
\input{related}
\up{3}
\section{Conclusion}
\up{3}
\input{conclusions}

% \bigskip
% \noindent{\bf Acknowledgment}
% The authors warmly thank Ernst Biersack for the precious help in
% reading an early version of this paper.  \bibliographystyle{plain}
% \bibliography{biblio}
 
%\up{2}
\begin{thebibliography}{10}
%\up{1}
{\scriptsize
\bibitem{BCCL08}
D.~Borsetti, C.~Casetti, C.~Chiasserini, and L.~Liquori.
\newblock {\em Heterogeneous Wireless Access Networks: Architectures and
  Protocols}, chapter {Content Discovery in Heterogeneous Mobile Networks}.
\newblock Sringer-Verlag, 2009.

\bibitem{castro_scribe:large-scale_2002}
M.~Castro, P.~Druschel, A.-M. Kermarrec, and A.~Rowstron.
\newblock {SCRIBE: A Large-Scale and Decentralized Application-Level Multicast
  Infrastructure}.
\newblock {\em {IEEE} Journal on Selected Areas in Communications {(JSAC)}},
  20, 2002.

\bibitem{cheng_bridging_2007}
L.~Cheng.
\newblock {Bridging Distributed Hash Tables in Wireless {Ad-Hoc} Networks}.
\newblock In {\em Global Telecommunications Conference, 2007. {GLOBECOM} '07.
  {IEEE}}, pages 5159--5163, 2007.

\bibitem{cheng2006tdh}
L.~Cheng, R.~Ocampo, K.~Jean, A.~Galis, C.~Simon, R.~Szabo, P.~Kersch, and
  R.~Giaffreda.
\newblock {Towards Distributed Hash Tables (De) Composition in Ambient
  Networks}.
\newblock {\em LNCS}, 4269:258, 2006.

\bibitem{Datta}
A.~Datta and K.~Aberer.
\newblock The\,challenges\,of\,merging\,two\,similar\,structured\,overlays:\,{A}\,tale\,of\,two\,networks.\,In\,{\em IWSOS},\,2006.

\bibitem{Biersack}
L.~G. Erice, E.~W. Biersack, K.~W. Ross, P.~A. Felber, and G.~U. Keller.
\newblock {Hierarchical P2P Systems}.
\newblock In {\em Euro-Par}, 2003.

% \bibitem{fonte_interdomain_2008}
% A.~Fonte, M.~Curado, and E.~Monteiro.
% \newblock {Interdomain Quality of Service Routing: Setting the Grounds for the
%   Way Ahead}.
% \newblock {\em Annals of Telecommunications}, 63(11):683--695, 2008.

\bibitem{furtado_multiple_2007}
P.~Furtado.
\newblock {Multiple Dynamic Overlay Communities and Inter-space Routing}.
\newblock {\em LNCS}, 4125:38, 2007.

\bibitem{junjiro_design_2006}
K.~Junjiro, W.~Naoki, and M.~Masayuki.
\newblock {Design and Evaluation of a Cooperative Mechanism for Pure P2P
  File-Sharing Networks}.
\newblock {\em {IEICE} Trans Commun {(Inst} Electron Inf Commun Eng)},
  {E89-B}(9):2319--2326, 2006.

\bibitem{kwon_synergy:overlay_2005}
M.~Kwon and S.~Fahmy.
\newblock {Synergy: an Overlay Internetworking Architecture}.
\newblock In {\em Proc. of International Conference on Computer Communications
  and Networks}, pages 401--406, 2005.

\bibitem{LBCC08}
L.~Liquori, D.~Borsetti, C.~Casetti, and C.~Chiasserini.
\newblock {An Overlay Architecture for Vehicular Networks}.
\newblock In {\em IFIP Networking, International Conference on Networking},
  volume 4982 of {\em LNCS}, pages 60--71. Springer, 2008.

\bibitem{LTB09}
L.~Liquori, C.~Tedeschi, and F.~Bongiovanni.
\newblock {BabelChord: a Social Tower of DHT-Based Overlay Networks}.
\newblock In {\em 14th Symposium on Computers and Communications (ISCC 2009)}.
  IEEE, 2009.
\newblock Short paper.

\bibitem{CAN}
\mbox{S.\,Ratnasamy,\,P.\,Francis,\,M.\,Handley,\,R.\,Karp,\,and\,S.\,Shenker.\,{A\,Scalable\,Content{-}Adressable\,Network}.\,In\,{\em SIGCOMM},\,2001.}

\bibitem{Pastry}
A.~Rowstron and P.~Druschel.
\newblock {Pastry: Scalable, Distributed Object Location and Routing for
  Large-Scale Peer-To-Peer Systems}.
\newblock In {\em Int. Conference on Distributed Systems Platforms
  (Middleware)}, 2001.

\bibitem{Haridi}
T.~M. Shafaat, A.~Ghodsi, and S.~Haridi.
\newblock Handling network partitions and mergers in structured overlay
  networks.
\newblock In {\em Proc. of P2P}, pages 132--139. IEEE Computer Society, 2007.

% \bibitem{siekkinen_beyondfuture_2007} M.~Siekkinen, V.~Goebel,
%   T.~Plagemann, {K.-A.} Skevik, M.~Banfield, and I.~Brusic.
%   \newblock {Beyond the Future Internet--Requirements of Autonomic
%     Networking Architectures to Address Long Term Future Networking
%     Challenges}.  \newblock In {\em International Workshop on Future
%     Trends of Distributed Computing Systems}, pages 89--98, 2007.

\bibitem{Chord}
I.~Stoica, R.~Morris, D.~Karger, M.~Kaashoek, and H.~Balakrishnan.
\newblock {Chord: A Scalable Peer-to-Peer Lookup service for Internet
  Applications.}
\newblock In {\em ACM SIGCOMM}, pages 149--160, 2001.
\bibitem{XuMH03} Z.~Xu, R.~Min, and Y.~Hu.  \newblock {HIERAS: A DHT
    Based Hierarchical P2P Routing Algorithm.}  \newblock In {\em
    ICPP}, 2003.  
%
}
\end{thebibliography}
 
 


% \appendix
  
% \begin{center}

% {\Large Referees can found the Synapse protocol code on}
% \bigskip

% \url{http://www-sop.inria.fr/teams/lognet/synapse/appendix}
% \end{center}


%\input{appendix}


\end{document}


