\documentclass[times,10pt,twocolumn]{article}
\usepackage[latin1]{inputenc}
%\usepackage{latex8}
\usepackage{times}
\usepackage{comment}
\usepackage{epsfig}
\usepackage{amssymb}
\usepackage{float}
\usepackage{boxedminipage}
\usepackage{algorithm}
\usepackage{url}
\urlstyle{sf}
\usepackage{fullpage}
\usepackage{alltt}
\usepackage[usenames]{color}
\usepackage{graphics}
%\usepackage{ulem}
\usepackage{verbatim}


%%% ENVIRONMENTS
\newtheorem{theorem}{Theorem}
\newtheorem{prop}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}{Example}
\newtheorem{remark}{Remark}

%%%
\newcommand{\ie}{\emph{i.e.}}
\newcommand{\eg}{\emph{e.g.}}
\newcommand{\verbi}[1]{{\small\texttt{#1}}}


%% Intra nos
\newcommand{\Ce} [1]{{[\color{cyan}{Cédric}}: {#1}]}
\newcommand{\Fr} [1]{{[\color{blue}{Francesco}} {#1}]}
\newcommand{\Lu} [1]{{[\color{red}{Luigi}}: {#1}]}
\newcommand{\RESP} [1]{{[\color{red}{RESP: #1}]}}


%%%% FORMATTING
\newcommand{\rew}[1]   {\hspace{-#1mm}}
\newcommand{\fwd}[1]   {\hspace{#1mm}}
\newcommand{\down}[1]  {\vspace{#1mm}}
\newcommand{\up}[1]    {\vspace{-#1mm}}


\include{algorithmic_header}

\sloppy

\date{\mbox{}}

%-------------------------------------------------------------------------
% take the % away on next line to produce the final camera-ready version
%\pagestyle{empty}
%-------------------------------------------------------------------------

%% High penalties for line and paragraph-breaking [Dan]
\pretolerance=2000 \binoppenalty=2000 \relpenalty=1500
%\interlinepenalty=150 \predisplaypenalty=10000 \postdisplaypenalty=400
\hbadness=5000 \hfuzz=2pt


\begin{document}

\title{On the Interconnection of Heterogeneous Overlay Networks}

\author{Francesco Bongiovanni \quad Luigi Liquori \quad Cédric
  Tedeschi \quad Bojan Marinkovic \\[2mm]
  INRIA Sophia Antipolis - M\'editerran\'ee, France\\
  {\small \url{surname.name@sophia.inria.fr}} }

\maketitle
\thispagestyle{empty}

\begin{abstract}
  The interconnection of overlay networks has been recently identified
  as a promising model for building the future Internet. Recent
  research has focused on design of mechanisms for building bridges
  between heterogeneous local overlay networks for cooperation.

  However, in this way, some simple \emph{meta}-protocols defining
  these bridges, and comprehensive quantitative studies of metrics
  such as \emph{satisfaction rate} or \emph{routing length} in such
  networks in the context of scalable information retrieval are still
  missing.

  The purpose of this paper is to presents Overnet, a \emph{meta}-protocol
  capturing the very essence of information retrieval over the
  interconnection of overlay networks. Overnet
  is based on co-located nodes filling the role of \emph{neural
    synapses} between networks. Second, we precisely capture the
  behavior of key metrics measuring this protocol, result of intensive
  simulations. Finally, we describe a new software prototype
  implementing such a concept based on the interconnection of Chord
  overlay networks, and exhibit some preliminary results of its actual
  deployment over the nationwide Grid'5000 platform.
\end{abstract}


\section{Introduction}
\input{intro}

\section{Background and Related Work\label{sec:relatedwork}}
\input{related}

\section{Meta-Protocol\label{sec:protocol}}
\input{protocol}

\section{Simulations\label{sec:simulations}}
\input{simulation}


\section{Software\label{sec:software}}
\input{software}


\section{Conclusion}
\input{conclusions}

\bibliographystyle{plain}
\bibliography{overnet}

\end{document}


% \AL \textbf{on receipt of} PUT(k,value) \textbf{from} ipsender \textbf{do}\alglabel{alg:lookupbegin}\hfill{\rm asking the peer for who is the responsible of key k}
% \AL  t = this.new_tag(ipsender);\hfill{\rm create a new unique tag for this lookup}
% \AL  \textbf{send} FIND(code,n,t,k,ipsender) \textbf{to} this.ip; \alglabel{alg:lookupend}\hfill{\rm send a FIND message to itself with TTL=n}
% \AL  \textbf{on receipt of} FOUND(f) \textbf{from} ipsender \textbf{do}\hfill{\rm received a FOUND message from ipsender}
% \AL   this.update_hotpeers(ipsender,f);\hfill{\rm update the hot peer list with ipsender at floor f}
% \AL   this.update_hotfloors(f,ipsender);\hfill{\rm update the hot floor list with f with peer ipsender}s
% \AL   \textbf{send} LOOKUP_TABLE(f,k) \textbf{to} ipsender \hfill{\rm send a LOOKUP\_TABLE message (omitted) at floor f on key k to ipsender}

% \AL \textbf{on receipt of} JOIN(f) \txtbf{from} ipsender \textbf{do}\hfill{\rm current peer invited by ipsender to join f}
% \AL   \textbf{if} this.good_join(f,ipsender)\hfill{\rm the join is ``good'' (peer's strategy)}
% \AL     this.references.insert(f,ipsender);\hfill{\rm insert references with ipsender at floor f}
% \AL     \textbf{send} JOINED(f) \textbf{to} ipsender;\hfill {\rm the peer ipsender has joined f}

% \AL \textbf{on receipt of} LEAVE(f) \textbf{from} ipsender \textbf{do}\hfill{\rm ip notify the current peer to leave f}
% \AL   this.references.delete(f,ipsender);\hfill{\rm delete references with ipsender at floor f}
% \AL   \textbf{send} LEFT(f) \textbf{to} ipsender;\hfill {\rm  the peer ipsender has left f}
% \end{alltt}}



% \begin{theorem}
%   With high probability, the number of nodes that must be contacted
%   to find a successor on a $N_1\times...\times N_k$-node network of
%   $k$ floors is $min(O(log(N_1)),...,O(log(N_k))$
% \end{theorem}

% \begin{theorem}
%   With high probability, the number of nodes that must be contacted
%   to (or to route back a success notification) on a
%   $N_1\times...\times N_k$-node network of $k$ floors is
%   $min(O(log(N_1)),...,O(log(N_k))$
% \end{theorem}

% \begin{theorem}
%   With high probability, and without (respectively with) Game-over
%   cut routing, the number of messages exchanged to find a successor
%   (or to route back a success notification) in a $N_1\times...\times
%   N_k$-node network of $k$ floors is $\sum_{i=1..k}O(log(N_i))$
%   (respectively $M \le \sum_{i=1..k}O(log(N_i))$).
% \end{theorem}



CONJECTURE

- With high probability and with time->infinity, an infinite number of
chord will "simulate" a fully connected graph, with routing complexity
-->_infty O(1), as in a plain array.


\section{Distributed Construction Mechanism}

At a given time, and within the default overlay (level $0$), a peer
$P$, which observed that a lot of its requests are satisfied by
another peer $Q$ may contact $Q$ for a possible collaboration. On
receipt, $Q$, which is a member of at least one overlay at level $1$,
enters in a negociation phase intended to decide whether $P$ may be a
neighbor of $Q$ on level $1$. This decision may be done on several
aspects, like \emph{capacities}, \emph{trust}, \emph{content}, etc.
$Q$ can asks its neighbors on level $1$ in order to obtain a consensus
on a possible membership of $P$. If $P$ has no membership at level
$1$, $P$ and $Q$ may initiate a new ring.

This mechanism can be easily extended to an arbitrary number of levels
(just replace $0$ by $m$ and $1$ by $m+1$. A peer may be the member of
several rings of the same level.

An $m$-ring (ring at level $m$) is always a refinement of an $m-1$
ring in which members consider the $m$ ring as more \emph{powerful}
(in their own point of view).

\section{Complexities}

The number of members in a ring may be limited. For instance, consider
that at level $1$, the members of a ring decide that no more than
$\log(n)$ peers should enter their ring, $n$ being the number of peers
at level $0$. As a consequence, routing table size and lookup length
at level $1$ will be $\log(log(n))$. If we apply the same rule at each
level, when the number of levels tends to infinity, the routing table
size and lookup length will be $\log^*(n)$, which increases very
(very) slowly.

In a more general point of view, we can consider that the maximum
number of members $N_m$ of a $m$-ring is always a function of $N_{m-1}$:

$$
N_m = f(N_{m-1})
$$

This function can be $\log()$ or the $\sqrt()$. Now, the number of
rings in which a peer acts at a given level may also be
limited. Finally, we have to find the right trade-off between the
number of levels, the size of rings at each level and the number of
rings a peer may belong to at a same level. (Thinking on this part...)




