\documentclass{llncs}
\usepackage{times,url,comment}
\usepackage{amsmath,amssymb,amsfonts,bbm}
\usepackage{graphicx,epsfig,epsf}
\usepackage{alltt}
\usepackage{url}
\usepackage{cite}
 
   
% mix and mac
\usepackage[latin1]{inputenc}
\usepackage{comment}
\usepackage{algorithm}
\usepackage[usenames]{color}

 

%%%
\newcommand{\ie}{i.e.}
\newcommand{\eg}{e.g.}
\newcommand{\vs}{vs.}

\newcommand{\verbi}[1]{{\small\texttt{#1}}}


%% Intra nos
\newcommand{\Ce} [1]{{[\color{cyan}{Cdric}}: {#1}]}
\newcommand{\Gi} [1]{{[\color{green}{Gigi}}: {#1}]}
\newcommand{\La} [1]{{[\color{cyan}{Laurent}}: {#1}]}
\newcommand{\Vi} [1]{{[\color{blue}{Vincenzo}}: {#1}]}

\newcommand{\RESP} [1]{{[\color{red}{RESP: #1}]}}




%% High penalties for line and paragraph-breaking [Dan]
\pretolerance=2000 \binoppenalty=2000 \relpenalty=1500
%\interlinepenalty=150 \predisplaypenalty=10000 \postdisplaypenalty=400
\hbadness=5000 \hfuzz=2pt 



%%%% FORMATTING
\newcommand{\rew}[1]   {\hspace{-#1mm}}
\newcommand{\fwd}[1]   {\hspace{#1mm}}
\newcommand{\down}[1]  {\vspace{#1mm}}
\newcommand{\up}[1]    {\vspace{-#1mm}}

\include{algorithmic_header}
 
 \title{CarPal: interconnecting overlay networks for a community-driven shared mobility} \up{4}
% %
 \author{Vincenzo Ciancaglini\inst{1} \and Luigi Liquori \inst{1} %\and C\'edric Tedeschi \inst{2}
     \and Laurent Vanni \inst{1}}

\institute{Institut National de Recherche en Informatique et
  Automatique, France\\
  Email: {\tt firstName.lastName@sophia.inria.fr} %\and
  %Universit\'e de Rennes I/INRIA, France\\ 
  %Email: {\tt Cedric.Tedeschi@inria.fr}
  }

\pagestyle{plain}
\sloppy

\begin{document}


\maketitle
  
\begin{abstract}\up{4}
  Car sharing has proven to be an effective solution 
  to reduce the amount of running vehicles by increasing the density of passengers per car
  amongst medium/big communities like schools or enterprises.
  However the success of such practice relies on the ability by the community to share and retrieve
  effectively information about travelers and itineraries.
  Structured overlay networks such as Chord or CAN has emerged recently as a flexible 
  solution to handle large amount of data without the use of high-end servers, 
  in a decentralized manner.
  In this paper we present CarPal, a proof-of-concept for a mobility sharing application that leverages
  a Distributed Hash Table to allow a community of people to spontaneously share trip information without 
  the costs of a centralized structure.
  The peer-to-peer architecture allows moreover the deployment on portable devices and opens new scenarios
  where trips can be updated in real time.
  Furthermore by the use of our Synapse protocol to interconnect different overlays/communities the success rate can be boosted
  up thus increasing the effectiveness of our solution. Some simulations results are shown to give
  a possible estimate of such effectiveness.

  \smallskip {\bf Keywords.} Peer to peer, overlay networks, case study,
  information retrieval, car sharing  \up{2}
\end{abstract}

  
\up{4}
\section{Introduction\label{sec:introduction}}
\up{3}
\input{introduction}
\up{3}
\section{Application architecture\label{sec:architecture}}
\up{3}
\input{architecture}
\up{3}
\section{Interconnecting multiple networks\label{sec:link}}
\up{3}
\input{link}
\up{3}
\section{Proof of concept\label{sec:proof}}
\up{3}
\input{proof}
\up{3}
\section{Experimental results\label{sec:experiences}}
\up{3}
\input{experiences}
\up{3}
\section{Conclusion and further work\label{sec:conclusion}}
\up{3}
\input{conclusion}

% \bigskip
% \noindent{\bf Acknowledgment}
% The authors warmly thank Ernst Biersack for the precious help in
% reading an early version of this paper.  \bibliographystyle{plain}
% \bibliography{biblio}
 
%\up{2}
\begin{thebibliography}{10}
%\up{1}
{\scriptsize
\bibitem{BCCL08}
D.~Borsetti, C.~Casetti, C.~Chiasserini, and L.~Liquori.
\newblock {\em Heterogeneous Wireless Access Networks: Architectures and
  Protocols}, chapter {Content Discovery in Heterogeneous Mobile Networks}.
\newblock Sringer-Verlag, 2009.

\bibitem{castro_scribe:large-scale_2002}
M.~Castro, P.~Druschel, A.-M. Kermarrec, and A.~Rowstron.
\newblock {SCRIBE: A Large-Scale and Decentralized Application-Level Multicast
  Infrastructure}.
\newblock {\em {IEEE} Journal on Selected Areas in Communications {(JSAC)}},
  20, 2002.

\bibitem{cheng_bridging_2007}
L.~Cheng.
\newblock {Bridging Distributed Hash Tables in Wireless {Ad-Hoc} Networks}.
\newblock In {\em Global Telecommunications Conference, 2007. {GLOBECOM} '07.
  {IEEE}}, pages 5159--5163, 2007.

\bibitem{cheng2006tdh}
L.~Cheng, R.~Ocampo, K.~Jean, A.~Galis, C.~Simon, R.~Szabo, P.~Kersch, and
  R.~Giaffreda.
\newblock {Towards Distributed Hash Tables (De) Composition in Ambient
  Networks}.
\newblock {\em LNCS}, 4269:258, 2006.

\bibitem{Datta}
A.~Datta and K.~Aberer.
\newblock The\,challenges\,of\,merging\,two\,similar\,structured\,overlays:\,{A}\,tale\,of\,two\,networks.\,In\,{\em IWSOS},\,2006.

\bibitem{Biersack}
L.~G. Erice, E.~W. Biersack, K.~W. Ross, P.~A. Felber, and G.~U. Keller.
\newblock {Hierarchical P2P Systems}.
\newblock In {\em Euro-Par}, 2003.

% \bibitem{fonte_interdomain_2008}
% A.~Fonte, M.~Curado, and E.~Monteiro.
% \newblock {Interdomain Quality of Service Routing: Setting the Grounds for the
%   Way Ahead}.
% \newblock {\em Annals of Telecommunications}, 63(11):683--695, 2008.

\bibitem{furtado_multiple_2007}
P.~Furtado.
\newblock {Multiple Dynamic Overlay Communities and Inter-space Routing}.
\newblock {\em LNCS}, 4125:38, 2007.

\bibitem{kwon_synergy:overlay_2005}
M.~Kwon and S.~Fahmy.
\newblock {Synergy: an Overlay Internetworking Architecture}.
\newblock In {\em Proc. of International Conference on Computer Communications
  and Networks}, pages 401--406, 2005.

\bibitem{LBCC08}
L.~Liquori, D.~Borsetti, C.~Casetti, and C.~Chiasserini.
\newblock {An Overlay Architecture for Vehicular Networks}.
\newblock In {\em IFIP Networking, International Conference on Networking},
  volume 4982 of {\em LNCS}, pages 60--71. Springer, 2008.

\bibitem{LTB09}
L.~Liquori, C.~Tedeschi, and F.~Bongiovanni.
\newblock {BabelChord: a Social Tower of DHT-Based Overlay Networks}.
\newblock In {\em 14th Symposium on Computers and Communications (ISCC 2009)}.
  IEEE, 2009.
\newblock Short paper.

\bibitem{CAN}
\mbox{S.\,Ratnasamy,\,P.\,Francis,\,M.\,Handley,\,R.\,Karp,\,and\,S.\,Shenker.\,{A\,Scalable\,Content{-}Adressable\,Network}.\,In\,{\em SIGCOMM},\,2001.}

\bibitem{Pastry}
A.~Rowstron and P.~Druschel.
\newblock {Pastry: Scalable, Distributed Object Location and Routing for
  Large-Scale Peer-To-Peer Systems}.
\newblock In {\em Int. Conference on Distributed Systems Platforms
  (Middleware)}, 2001.

\bibitem{Haridi}
T.~M. Shafaat, A.~Ghodsi, and S.~Haridi.
\newblock Handling network partitions and mergers in structured overlay
  networks.
\newblock In {\em Proc. of P2P}, pages 132--139. IEEE Computer Society, 2007.

% \bibitem{siekkinen_beyondfuture_2007} M.~Siekkinen, V.~Goebel,
%   T.~Plagemann, {K.-A.} Skevik, M.~Banfield, and I.~Brusic.
%   \newblock {Beyond the Future Internet--Requirements of Autonomic
%     Networking Architectures to Address Long Term Future Networking
%     Challenges}.  \newblock In {\em International Workshop on Future
%     Trends of Distributed Computing Systems}, pages 89--98, 2007.

\bibitem{Chord}
I.~Stoica, R.~Morris, D.~Karger, M.~Kaashoek, and H.~Balakrishnan.
\newblock {Chord: A Scalable Peer-to-Peer Lookup service for Internet
  Applications.}
\newblock In {\em ACM SIGCOMM}, pages 149--160, 2001.
\bibitem{XuMH03} Z.~Xu, R.~Min, and Y.~Hu.  \newblock {HIERAS: A DHT
    Based Hierarchical P2P Routing Algorithm.}  \newblock In {\em
    ICPP}, 2003.  
%
}
\end{thebibliography}

\end{document}


